18th International Satisfiability Modulo Theories Competition (SMT-COMP 2023): Rules and Procedures

### 2023-04-26 rules/rules23.tex
SMT-COMP23 rules: changes to the wall-clock and CPU time scores.

\item {\bf Wrapper Script for \prooftrack.}
   The wrapper script is changed to remove very large proofs and
   to cut very large error/debug output.
%
   \rationale{Last Year, the \prooftrack produced 800~GB of output, most
   of that stemming from a few benchmark/solver pairs. These cannot be
   removed without losing the whole proof track job.   It also makes
   downloading and sharing the result much harder.}
\end{itemize}

@@

The \textbf{parallel benchmark score} of a solver is a quadruple $\langle
e, n, w, c\rangle$, with
\begin{itemize}[noitemsep]
  \vspace{-1ex}
  \item \makebox[5em][l]{$e \in \{0, 1\}$}
    number of erroneous results (usually~$e = 0$)
  \item \makebox[5em][l]{$0 \leq n \leq N$}
    number of correct results (resp.~\emph{reduction} for the \ucoretrack)
  \item \makebox[5em][l]{$w \in [0,T]$}
    wall-clock time in seconds (real-valued)
  \item \makebox[5em][l]{$c \in [0, mT]$}
    CPU time in seconds (real-valued)
\end{itemize}

@@

\header{Wall-Clock Time Score ($\mathbf{w}$).}
The (real-valued) wall-clock time in seconds, until time limit $T$ or the
solver process terminates.

\header{CPU Time Score ($\mathbf{c}$).}
The (real-valued) CPU time in seconds, measured across all $m$ cores
until time limit $mT$ is reached or the solver process
terminates.

@@

The parallel score as defined above favors parallel solvers, which may utilize
all available processor cores.  To evaluate sequential performance, we derive a
\textbf{sequential score} by imposing a \emph{virtual} CPU time limit equal to
the wall-clock time limit~$T$.  A solver result is taken into consideration for
the sequential score only if the solver process terminates \emph{within} this
CPU time limit.  More specifically, for a given parallel performance $\langle
e, n, w, c\rangle$, the corresponding sequential performance is defined
as~$\langle e_S, n_S, c_S\rangle$, where
\begin{itemize}
\item $e_S = 0$ and $n_S = 0$ if $c > T$, and $e_S = e$ and $n_S = n$
  otherwise,
\item $c_S = \min\ \{c, T\}$.\footnote{Under this
  measure, a solver should not benefit from using multiple processor
  cores.  Conceptually, the sequential performance should be (nearly)
  unchanged if the solver was run on a single-core processor, up to a
  time limit of~$T$.}
\end{itemize}

@@

\header{Sound Solver.}
A solver is \emph{sound} on benchmarks with \emph{known status} for a division
if its parallel performance (Section~\ref{sec:benchmark-scoring}) is of the
form $\langle 0, n, w, c\rangle$ for each benchmark in the division, i.e., if
it did not produce any erroneous results.

@@

The parallel score for a division is computed for \emph{all} tracks.  It is
defined for a participating solver in a division with $M$ benchmarks as the sum
of all the individual parallel benchmark scores:
$$\sum_{b\in M} \langle e_b , n_b , w_b, c_b\rangle$$.

\noindent
A parallel division score $\langle e, n, w, c\rangle$ is better than a parallel
division score $\langle e', n', w', c'\rangle$ iff $e < e'$ or ($e = e'$ and $n
> n'$) or ($e = e'$ and $n = n'$ and $w < w'$) or ($e = e'$ and $n = n'$ and $w
= w'$ and $c < c'$).  That is, fewer errors takes precedence over more correct
solutions, which takes precedence over less wall-clock time taken, which takes
precedence over less CPU time taken.

@@

The sequential score for a division is computed for \emph{all} tracks
\emph{except} the \inctrack, \paralleltrack, and \cloudtrack.
\footnote{Since incremental track benchmarks may be partially
solved, defining a useful sequential performance for the incremental track
would require information not provided by the parallel performance, e.g.,
detailed timing information for each result.  Due to the nature of
\paralleltrack and \cloudtrack we will not consider the sequential
scores}.  It is defined for a
participating solver in a division with $M$ benchmarks as the sum of all the
individual sequential benchmark scores:
$$\sum_{b\in M} \langle e_b^s, n_b^s, w_b^s, c_b^s\rangle$$.

@@

Let $\langle e^s, n^s, w^s, c^s \rangle$ be the parallel division score
for solver $s$ (for a given scoring system, i.e., $n$ is either number of correct
results or reduction).
If the division error score $e^s > 0$, then solver $s$ is considered unsound
and excluded from the ranking.
If the number of sound competitive solvers~$S$ in a division $D$ is $|S| \leq 2$,
the division is excluded from the ranking.

Let $\langle e_b^s, n_b^s, w_b^s, c_b^s \rangle$ be the parallel benchmark
score for benchmark $b$ and solver $s$ (for a given scoring system).
The virtual best solver \emph{correctness score} for a division $D$ with
competitive sound solvers $S$ is given as
\[
\mathit{vbss}_n(D,S) = \sum_{b \in D} {\sf max}\{ n_b^s \mid s \in S ~\mathit{and}~ n_b^s > 0 \}
\]
where the maximum of an empty set is 0 (i.e., no contribution if a benchmark
is unsolved).

>>>>

\item {\bf Wrapper Script for \prooftrack.}
   The wrapper script is changed to remove very large proofs and
   to cut very large error/debug output.
%
   \rationale{Last Year, the \prooftrack produced 800~GB of output, most
   of that stemming from a few benchmark/solver pairs. These cannot be
   removed without losing the whole proof track job.   It also makes
   downloading and sharing the result much harder.}

\item {\bf Scoring.}  \emergencystretch.5cm We adjusted the wall-clock and 
CPU time scores so only the benchmarks that are correctly solved within the 
time limit $T$ are counted.
%
  \rationale{We noticed that in the previous scoring unintended results 
  did occur because timeouts were scored worse than aborts and could 
  overshadow the times of correctly solved problems. For instance, 
  solver A that never aborts could lose to solver B that frequently aborts 
  although A solved exactly the same problems B could solve and A was always 
  faster on the solved problems than B.}
\end{itemize}

@@

The \textbf{parallel benchmark score} of a solver is a quadruple $\langle
e, n, w, c\rangle$, with
\begin{itemize}[noitemsep]
  \vspace{-1ex}
  \item \makebox[6em][l]{$e \in \{0, 1\}$}
    number of erroneous results (usually~$e = 0$)
  \item \makebox[6em][l]{$0 \leq n \leq N$}
    number of correct results (resp.~\emph{reduction} for the \ucoretrack)
  \item \makebox[6em][l]{$\it{aw} \in [0,T]$}
    actual wall-clock time in seconds (real-valued)
  \item \makebox[6em][l]{$w \in [0,T]$}
    wall-clock time score in seconds (real-valued)
  \item \makebox[6em][l]{$\it{ac} \in [0, mT]$}
    actual CPU time in seconds (real-valued)
  \item \makebox[6em][l]{$c \in [0, mT]$}
    CPU time score in seconds (real-valued)
\end{itemize}

@@

\header{Actual Wall-Clock Time ($\mathbf{aw}$).}
The actual (real-valued) wall-clock time in seconds, until time limit $T$ or the
solver process terminates.

\header{Wall-Clock Time Score ($\mathbf{w}$).}
For the \maintrack, \ucoretrack, \mvaltrack, \paralleltrack, and
\cloudtrack, the wall-clock time score $w$ is the same as 
the actual (real-valued) wall-clock time $\it{aw}$, 
except that it is zero if the benchmark was not correctly solved within the time limit $T$, i.e., 
$w = 0$ if $e = 1$, the process did not terminate within the time limit $T$, or 
it did return unknown or an unknown result.
For the \inctrack, the wall-clock time score $w$ 
is the (real-valued) wall-clock time in seconds until the process returned the last correct result for a \akey{check-sat} command within the time limit;
this means especially that $w = 0$ is zero if no (correct) result was returned for the first \akey{check-sat} command within the time limit.

\header{Actual CPU Time ($\mathbf{ac}$).}
The (real-valued) CPU time in seconds, measured across all $m$ cores
until time limit $mT$ is reached or the solver process
terminates.

\header{CPU Time Score ($\mathbf{c}$).}
For the \maintrack, \ucoretrack, \mvaltrack, \paralleltrack, and
\cloudtrack, the CPU time score $c$ is the same as 
the actual (real-valued) CPU time $\it{ac}$, 
except that it is zero if the benchmark was not correctly solved within the time limit $mT$, i.e., 
$c = 0$ if $e = 1$, the process did not terminate within the time limit $mT$, or 
it did return unknown or an unknown result.
For the \inctrack, the CPU time score $c$ 
is the (real-valued) CPU time in seconds until the process returned the last correct result for a \akey{check-sat} command within the time limit;
this means especially that $c = 0$ is zero if no (correct) result was returned for the first \akey{check-sat} command within the time limit.

@@

The parallel score as defined above favors parallel solvers, which may utilize
all available processor cores.  To evaluate sequential performance, we derive a
\textbf{sequential score} by imposing a \emph{virtual} CPU time limit equal to
the wall-clock time limit~$T$.  A solver result is taken into consideration for
the sequential score only if the solver process terminates \emph{within} this
CPU time limit.  More specifically, for a given parallel performance $\langle
e, n, \it{aw}, w, \it{ac}, c\rangle$, the corresponding sequential performance is defined
as~$\langle e_S, n_S, c_S\rangle$, where
\begin{itemize}
\item $e_S = 0$, $n_S = 0$, and $c_S = 0$ if $c > T$;
\item $e_S = e$, $n_S = n$, and $c_S = c$
  otherwise.\footnote{Under this
  measure, a solver should not benefit from using multiple processor
  cores.  Conceptually, the sequential performance should be (nearly)
  unchanged if the solver was run on a single-core processor, up to a
  time limit of~$T$.}
\end{itemize}

@@

\header{Sound Solver.}
A solver is \emph{sound} on benchmarks with \emph{known status} for a division
if its parallel performance (Section~\ref{sec:benchmark-scoring}) is of the
form $\langle 0, n, \it{aw}, w, \it{ac}, c\rangle$ for each benchmark in the division, i.e., if
it did not produce any erroneous results.

@@

The parallel score for a division is computed for \emph{all} tracks.  It is
defined for a participating solver in a division with $M$ benchmarks as the sum
of all the individual parallel benchmark scores:
$$\sum_{b\in M} \langle e_b , n_b , \it{aw}_b, w_b, \it{ac}_b, c_b\rangle$$.

\noindent
A parallel division score $\langle
e, n, \it{aw}, w, \it{ac}, c\rangle$ is better than a parallel
division score\newline $\langle e', n', \it{aw}', w', \it{ac}', c'\rangle$ iff $e < e'$ or ($e = e'$ and $n
> n'$) or ($e = e'$ and $n = n'$ and $w < w'$) or ($e = e'$ and $n = n'$ and $w
= w'$ and $c < c'$).  That is, fewer errors takes precedence over more correct
solutions, which takes precedence over less wall-clock time taken, which takes
precedence over less CPU time taken.

@@

The sequential score for a division is computed for \emph{all} tracks
\emph{except} the \inctrack, \paralleltrack, and \cloudtrack.
\footnote{Since incremental track benchmarks may be partially
solved, defining a useful sequential performance for the incremental track
would require information not provided by the parallel performance, e.g.,
detailed timing information for each result.  Due to the nature of
\paralleltrack and \cloudtrack we will not consider the sequential
scores}.  It is defined for a
participating solver in a division with $M$ benchmarks as the sum of all the
individual sequential benchmark scores:
$$\sum_{b\in M} \langle e_b^s, n_b^s, \it{aw}_b^s, w_b^s, \it{ac}_b^s, c_b^s\rangle$$.

@@

Let $\langle e^s, n^s, \it{aw}^s, w^s, \it{ac}^s, c^s \rangle$ be the parallel division score
for solver $s$ (for a given scoring system, i.e., $n$ is either number of correct
results or reduction).
If the division error score $e^s > 0$, then solver $s$ is considered unsound
and excluded from the ranking.
If the number of sound competitive solvers~$S$ in a division $D$ is $|S| \leq 2$,
the division is excluded from the ranking.

Let $\langle e_b^s, n_b^s, \it{aw}_b^s, w_b^s, \it{ac}_b^s, c_b^s \rangle$ be the parallel benchmark
score for benchmark $b$ and solver $s$ (for a given scoring system).
The virtual best solver \emph{correctness score} for a division $D$ with
competitive sound solvers $S$ is given as
\[
\mathit{vbss}_n(D,S) = \sum_{b \in D} {\sf max}\{ n_b^s \mid s \in S ~\mathit{and}~ n_b^s > 0 \}
\]
where the maximum of an empty set is 0 (i.e., no contribution if a benchmark
is unsolved).
